I Compensate, therefore I Am \\ (accurate for DNN verification)

### 2024-01-27 Paper/proofs.tex
try

	We have $\val'_{\boldsymbol{x}_J}(n)=\Val_{\boldsymbol{x}^*_I,\boldsymbol{x}_J}(n)$ 
	for every node $n$ of $D'$. All the ReLU nodes of $D'$ are in $X$, by definition of $X$.
Thus $\MILP_X$ will be fully accurate in $D'$. Let $\beta'$ denote its upper bound.
We have $\beta'=\max_{\vx{_J}} (\val'_{\vx_{J}}(z)) = 
\Val_{\boldsymbol{x}^*_I,\boldsymbol{x}_J}(n) = \max(z)$ by Corrolary \ref{corr:main}.
Now, in $D$, $\MILP_X$ will use simple LP on $D_I$, which suffices to get the upper bound $\val_{\vx^*_I}(n)=\max(n)$ for all $n$ in $D_I$ and the values will be pushed as bias in $D'$. Therefore, $\beta=\beta'=\max(z)$.

The case for $\alpha=min(z)$ is similar. \qed

>>>>

	We have $\val'_{\boldsymbol{x}_J}(n)=\Val_{\boldsymbol{x}^*_I,\boldsymbol{x}_J}(n)$ 
	for every node $n$ of $D'$. All the ReLU nodes of $D'$ are in $X$, by definition of $X$.
Thus $\MILP_X$ will be fully accurate in $D'$. Let $\beta'$ denote its upper bound.
We have $\beta'=\max_{\vx{_J}} (\val'_{\vx_{J}}(z)) = 
\Val_{\boldsymbol{x}^*_I,\boldsymbol{x}_J}(n) = \max(z)$ by Corollary \ref{corr:main}.
Now, in $D$, $\MILP_X$ will use simple LP on $D_I$, which suffices to get the upper bound $\val_{\vx^*_I}(n)=\max(n)$ for all $n$ in $D_I$ and the values will be pushed as bias in $D'$. Therefore, $\beta'=\max(z)$.

We now prove that $\beta=\beta'$, which terminates the proof, as The case for $\alpha=min(z)$ is similar.

We prove by induction from the input layer to higher layers that the upper bound of node $n$ in $D'$, is greater than or equal to the upper bound in $D$; and similarly for the lower bound. We use  $\Val^{D}_{x_J^0}(n)$ to denote the range of possible values for node $n$ in  model $D$ or $D'$ when $x_J=x_J^0$. 
This may be a single number or an interval. 
Denote by $\beta_{x_J^0}(m)$ (resp $\beta'_{x_J^0}(m)$) the upper bound computed by $\MILP_X$ 
for $m$ in $D$ (resp. $D'$) when the $J$ input is fixed to be ${x_J^0}$.

For any input $x_J=x_J^0$, we prove $\beta'_{x_J^0} \geq \beta_{x_J^0}$ by induction on $n$:

\begin{align*}
	\beta'_{x_J^0}(n) = & {bias}_n+\sum_{m\in B_{pure}} W_{mn} \beta'(\hat{m})
	+\sum_{m\notin B_{pure}} W_{mn} (\beta'_{x_J^0}(\hat{m}))\\
(\text{by induction})\geq & {bias}_n+\sum_{m\in B_{pure}} \max(\ReLU(W_{mn}m))+\sum_{m\notin B_{pure}} 
\UB(\ReLU(W_{mn}\Val^{D}_{x_J^0}(m)))\\
= & {bias}_n+\sum_{m\in B_{pure}} \UB(\mathrm{AppB}(W_{mn}))+\sum_{m\notin B_{pure}}  \UB(\ReLU(W_{mn}\Val^{D}_{x_J^0}(m)))\\
\geq & \UB(\Val^{D}_{x_J^0}(n)), \text{when } S(n)=1
\end{align*}

Hence, using the $\max$ over ${x_J^0}$, 
we will have $\max(z) = \beta'\geq \beta \geq \max(z)$, and hence $\beta=\beta'=\max(z)$.

\qed
